Supplementary material: The increasing cost of happiness

### 2021-06-24 src/draft-html.Rmd
clean up html

---
title: "The increasing cost of happiness"
author: "R.W.Morris^1,2^, N.Kettlewell^2,3,4^  & N.Glozier^1,2^"
bibliography: ../src/references.bib
csl: ../src/elsevier-harvard.csl
output:  
  word_document:
    reference_docx: ../src/Rmarkdown-for-Word-styles.docx
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "The increasing cost of happiness"
author: "R.W.Morris^1,2^, N.Kettlewell^2,3,4^  & N.Glozier^1,2^"
bibliography: ../src/references.bib
csl: ../src/elsevier-harvard.csl
output:  
  html_document:
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

### 2021-06-24 src/supplementary-html.Rmd
clean up html

---
title: "Supplementary material: The increasing cost of happiness"
bibliography: ../src/references.bib
csl: ../src/elsevier-harvard.csl
output:  
  word_document:
    reference_docx: ../src/Rmarkdown-for-Word-styles.docx
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Supplementary material: The increasing cost of happiness"
bibliography: ../src/references.bib
csl: ../src/elsevier-harvard.csl
output:  
  html_document:
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---
